A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-01-24 highlights.tex
Updates from Overleaf

A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
...

@@

\subsection{2-4}
2-4) Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
Answer
We modified the introduction ...
https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications

@@

x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
We could provide more evidence to support the prognostic impact of these candidate genes.

>>>>

there is survival feature:
A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
...

@@

\subsection{2-4}
2-4) Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.
Answer
*** We modified the introduction according to reviewer's comment...
https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications

@@

%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
We provide more evidences mentioned above to support the prognostic impact of these candidate genes. It needs to be further validated.
